hbm_paper_results

### 2024-02-19 paper_replication_results.Rmd
summarise results

Rmd to show and get feedback on planned for results & figures for the combatLS paper. Currently thinking I'll have centile score results be the focus of the paper and keep z-scores for the supplement.

@@

```{r}
data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives"

@@

#plotting info from dk atlas
dk.parc <- dk$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()
```

# Define Functions

Pairwise T tests: within each feature, run paired t tests (welch's test on ranks) pairwise on each possible pairing of combat configs and return as a single dataframe, with FDR correction for all feature + cf pair combos. Currently runs on magnitude (abs val) of centile diffs, but can be run on other metrics by redefining `feature_list` Recommended for use with mclapply across list of dataframes. Optional argument to correct for more comparisons (e.g. fdr-correct across an entire list of dataframes) using `comp_multiplier` arg.

```{r}
#define function
pheno_abs.diff.list <- paste0("abs.diff_", pheno_list)

centile.t.tests <- function(df, feature_list=pheno_abs.diff.list, comp_multiplier=1){
  #initialize empty dfs to store outputs
  t.df <- data.frame("pheno" = character(),
                     "group1" = character(),
                     "group2" = character(),
                     "p.value" = double())
  #run tests
  attach(df)
  for (pheno in feature_list) {
    df.pairwise.t <- tidy(pairwise.rank.welch.t.test(x=df[[pheno]], g=df[["dataset"]], paired = TRUE, p.adj = "none"))
    df.pairwise.t$pheno <- pheno
    t.df <- rbind(t.df, df.pairwise.t)
  }
  n_comp <- nrow(t.df)

  #apply fdr correction
  t.df <- t.df %>%
    dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = (n_comp*comp_multiplier)),
           sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                               p.val_fdr >= 0.05 ~ FALSE),
           pheno = sub("abs.diff_", "", pheno)) %>%
    unite(comp, c("group1", "group2")) %>%
   dplyr::mutate(comp = as.factor(comp))

  t.df.sum <- t.df %>%
    group_by(comp) %>%
    dplyr::summarize(n_sig_regions = sum(sig_fdr),
              min_pval = min(p.val_fdr),
              max_pval = max(p.val_fdr)) %>%
    ungroup() %>%
    as.data.frame()
  return(t.df.sum)
  #detach()
}

### EXAMPLE:
# perm_t.tests <- mclapply(perm_diffs, centile.t.tests, mc.preschedule = FALSE)
# names(perm_t.tests) <- n_perm_list
# cent_t.tests.p <- bind_rows(perm_t.tests, .id = "column_label")
```

Within each combat config, test if there are significant differences in M and F subject's mean abs. centile error. Can test mean (not abs) centile errors, Z errors, etc, using `to_test` arg. FDR corrects for number of datasets tested

```{r}
sex.bias.t.tests <- function(df, to_test = "mean_cent_abs.diff", comp_multiplier=1){

  #conduct t test
  df.sex.t <- df %>%
    group_by(dataset) %>%
    summarise(p.value = tidy(rank.welch.t.test.formula(formula=as.formula(paste(to_test, "~ sex")), paired = FALSE, p.adj = "none"))$p.value,
              sex_diff = tidy(rank.welch.t.test.formula(formula=as.formula(paste(to_test, "~ sex")), paired = FALSE, p.adj = "none"))$estimate,
              t.stat = tidy(rank.welch.t.test.formula(formula=as.formula(paste(to_test, "~ sex")), paired = FALSE, p.adj = "none"))$statistic,
              df = tidy(rank.welch.t.test.formula(formula=as.formula(paste(to_test, "~ sex")), paired = FALSE, p.adj = "none"))$parameter) %>%
    ungroup()

  #apply fdr correction
  n_comp=length(unique(df$dataset))
  df.sex.t <- df.sex.t %>%
    dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = (n_comp*comp_multiplier)), #use comp_multiplier if using fun with lapply
           sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                               p.val_fdr >= 0.05 ~ FALSE))
  return(df.sex.t)
  #detach()
}

# tidy(rank.welch.t.test.formula(formula=mean_cent_abs.diff ~ sex, data= ratio_subj_list[[1]], paired = FALSE, p.adj = "none"))
# rank.welch.t.test.formula(formula=mean_cent_abs.diff ~ sex, data= ratio_subj_list[[1]], paired = FALSE, p.adj = "none")
```

modifying to test for sex-biases w/in feature rather than mean centiles

```{r}
pheno_diff_list <- paste0("diff_", pheno_list)
sex.bias.feat.t.tests <- function(df, feature_list=pheno_diff_list, comp_multiplier=1){

  #initialize empty df to store outputs
  t.df <- data.frame("dataset" = character(),
                     "pheno" = character(),
                     "p.value" = double(),
                     "sex_diff" = double(),
                     "t.stat" = double(),
                     "df" = double())
  attach(df)
  for (pheno in feature_list) {
  #print(paste("t-test:", pheno))

  #conduct t test
  df.sex.t <- df %>%
    group_by(dataset) %>%
    summarise(p.value = tidy(rank.welch.t.test.formula(formula=as.formula(paste(pheno, "~ sex")), paired = FALSE, p.adj = "none"))$p.value,
              sex_diff = tidy(rank.welch.t.test.formula(formula=as.formula(paste(pheno, "~ sex")), paired = FALSE, p.adj = "none"))$estimate,
              t.stat = tidy(rank.welch.t.test.formula(formula=as.formula(paste(pheno, "~ sex")), paired = FALSE, p.adj = "none"))$statistic,
              df = tidy(rank.welch.t.test.formula(formula=as.formula(paste(pheno, "~ sex")), paired = FALSE, p.adj = "none"))$parameter) %>%
    ungroup()

  df.sex.t$pheno <- sub("diff_", "", pheno)

  #append to full df
  t.df <- rbind(t.df, df.sex.t)
  }
  detach(df)

  #also get medians for m and f
  med_df <- df %>%
  dplyr::group_by(dataset, sex) %>%
    summarise_at(feature_list, median) %>%
    ungroup() %>%
    pivot_longer(cols = starts_with("diff_"), names_to="pheno", names_prefix="diff_") %>%
    pivot_wider(names_from = sex, values_from=value, names_glue = "med_{sex}") %>%
    mutate(median_sex_diff = (med_Male - med_Female)) %>%
    ungroup()

  #combine feature dfs
  result_df <- left_join(t.df, med_df)

  #apply fdr correction
  n_comp=length(unique(df$dataset))*length(feature_list)
  result_df <- result_df %>%
    dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = (n_comp*comp_multiplier)), #use comp_multiplier if using fun with lapply
           sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                               p.val_fdr >= 0.05 ~ FALSE),
           dataset=as.factor(dataset))

  # #summarize
  # df.sex.t.sum <- df.sex.t %>%
  #   group_by(dataset) %>%
  #   dplyr::summarize(n_sig_regions = sum(sig_fdr),
  #             min_pval = min(p.val_fdr),
  #             max_pval = max(p.val_fdr)) %>%
  #   ungroup() %>%
  #   as.data.frame()

  return(result_df)

}
# sex.bias.feat.t.tests(diffs.df, feature_list = global.diff)
```

Test for linear relationships between subject's actual centile score (calculated from raw data) and how much that score is affected by different combat methods.

```{r}
extremeness.lm <- function(df, f, comp_multiplier=1){

  #conduct t test
  df.lm <- df %>%
    group_by(dataset) %>%
    #returns values for last (highest order) predictor
    summarise(p.value = tail(tidy(lm(as.formula(f)))$p.value, n=1),
              estimate = tail(tidy(lm(as.formula(f)))$estimate, n=1),
              t.stat = tail(tidy(lm(as.formula(f)))$statistic[2], n=1),
              std.error = tail(tidy(lm(as.formula(f)))$std.error[2]), n=1) %>%
    ungroup()
  n_comp=length(unique(df$dataset))

  #apply fdr correction
  df.lm <- df.lm %>%
    dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = (n_comp*comp_multiplier)),
           sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                               p.val_fdr >= 0.05 ~ FALSE))
  return(df.lm)
  #detach()
}

# tidy(lm(mean_centile ~ mean_cent_diff, data= ratio_subj_list[[1]]))
# summary(lm(mean_centile ~ mean_cent_diff, data= ratio_subj_list[[1]]))
```

plot w/in feature average centile errors

```{r}
#define plotting
plot.cent.diffs <- function(df){
mean.diffs.long <- df %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  dplyr::summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  dplyr::select(-ends_with(".z")) %>% #drop z-score cols
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

cent.diffs.plot <- mean.diffs.long %>%
  dplyr::filter(dataset != "raw") %>%
  mutate(centile_abs.diff = centile_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_histogram(aes(x=centile_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_wrap(~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values=dataset_colors, name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y= "Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centile scores across ComBat processing pipelines")

print(cent.diffs.plot)
}
```

# Replication

@@

```{r}
raw_files <- list.files(path = paste0(data_path, "/ukb_perm"), pattern = "_diffs.csv", full.names = TRUE) %>% unlist()

@@

```{r}
raw_files <- list.files(path = paste0(data_path, "/ukb_perm"), pattern = "_subj_pred.csv", full.names = TRUE)

@@

Do each feature's centile scores change based on combat version?

```{r, warning=FALSE}
#apply
perm_t.tests <- mclapply(diffs_perm.list, centile.t.tests, mc.preschedule = FALSE, comp_multiplier=length(diffs_perm.list))
names(perm_t.tests) <- n_perm_list
cent_t.tests.p <- bind_rows(perm_t.tests, .id = "column_label")
fwrite(cent_t.tests.p, file="derivatives/ukb_perm/centile_t.tests.csv")
```

```{r}
cent_t.tests.p %>%
  group_by(comp) %>%
  dplyr::summarize(n_sig_min=min(n_sig_regions),
            n_sig_max = max(n_sig_regions),
            n_sig_mean = mean(n_sig_regions))
```

Little plots

```{r}
lapply(diffs_perm.list, plot.cent.diffs)
```

@@

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
cent.diffs.v.plot <- perm_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=dataset, y=mean_cent_abs.diff, fill=perm), scale="count") +
  labs(y= "Mean Magnitude Centile Error", x = "ComBat Configurations") +
  scale_x_discrete(labels=c(dataset_names)) +
  guides(fill=guide_legend(title="Sampling \nPermutation")) + 
  ggtitle("Fig 1B. Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations replicated 10x")
cent.diffs.v.plot
ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot)
```

@@

```{r, warning=FALSE}
sex_t_tests_in_feat.df <- mclapply(diffs_perm.list, sex.bias.feat.t.tests, mc.preschedule = FALSE, comp_multiplier=length(diffs_perm.list))

#also get summary
sex_t_tests_in_feat.df %>%
    group_by(dataset) %>%
    dplyr::summarize(n_sig_regions = sum(sig_fdr),
              min_pval = min(p.val_fdr),
              max_pval = max(p.val_fdr)) %>%
    ungroup() %>%
    as.data.frame()
```

@@

*come back to this*

*need to look at distribution to check for skew!*

## SCALE EFFECTS OF SEX

fix age, get diff between male and female pred. variance

```{r}
# combined_preds.p <- data.frame()
get.var <- function(x){
  df <- data.frame() #new empty dataframe
  var.csvs.p <- list.files(path = permutation_path, pattern = paste0(x, ".+_variance.csv"), full.names = TRUE)
  for (file in var.csvs.p) {
    # Read each CSV file
    data <- fread(file)

    # Add a "Source_File" column with the file name
    data <- data %>%
      mutate(Source_File = as.factor(basename(file)),
             perm = as.factor(x)) %>%
      mutate(dataset = gsub("_data|_variance.csv|perm-|[0-9]|-", "", Source_File),
             sex_standard = sex_effect/f.var,
             pheno = as.character(pheno))

    # Bind the data to the combined dataframe
    df <- bind_rows(df, data, .id = "File_ID")
  }
  return(df)
}

perm_var <- mclapply(n_perm_list, get.var, mc.preschedule = FALSE)
perm_var.all <- bind_rows(perm_var, .id = "column_label")
```

maybe better to get sex_summary.csv - just need significance

```{r}
#get summary df for p vals, plotting
sigma.sex.df <- fread("derivatives/ukb_perm_csvs/sex_summary.csv", stringsAsFactors = TRUE) %>%
  dplyr::select(-V1) %>%
  mutate(perm = gsub("ukb-CN-data-agefilt-|-raw|-cf|.lm|.gam|.gamlss|-data", "", dataset),
         dataset = gsub("-data", "", dataset),
         dataset = gsub("simsites|ukb-CN-agefilt-|perm-|[0-9]", "", dataset),
         dataset = gsub("-", "", dataset),
         #dataset = as.character(dataset),
         pheno = as.character(pheno)) %>%
  mutate(dataset = factor(dataset, levels = unique(dataset), ordered = FALSE),
         perm = factor(perm, levels = unique(perm), ordered=FALSE)) %>%
  #mutate(dataset = relevel(dataset, ref= "raw")) %>%
  dplyr::filter(parameter == "sigma" & term == "sexMale") %>%
  dplyr::select(mod_name, pheno, dataset, pheno_cat, label, sig.sum_bf.corr, perm, sig.drop_bf.corr)

perm_var_info <- inner_join(perm_var.all, sigma.sex.df)
```

```{r}
  sex_effect_plot <- perm_var_info %>%
    mutate(sex_standard = case_when(sig.drop_bf.corr == TRUE ~ sex_standard,
                                    sig.drop_bf.corr == FALSE ~ 0)) %>% #only significant effects
    ggplot() +
    geom_col(aes(x=pheno, y=sex_standard, fill=dataset)) +
    facet_wrap(~perm, ncol=5) +
    ggtitle(paste("Standardized effect of male sex on variance")) +
    theme(axis.text.x = element_blank())

    ggsave(paste0("figs/male_variance_perms.jpeg"), sex_effect_plot)
    print(sex_effect_plot)
```

>>>>

@@

```{r}
data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_perm"

@@

#plotting info from dk atlas
dk.parc <- dk$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()
#write out new dk atlas w/o medial wall
dk_nomed <- dk
dk_nomed$data <- dk_nomed$data %>%
  dplyr::filter(!is.na(region) & region !="corpus callosum")
```

@@

```{r, eval=FALSE}
raw_files <- list.files(path = data_path, pattern = "_diffs.csv", full.names = TRUE) %>% unlist()

@@

```{r}
raw_files <- list.files(path = data_path, pattern = "_subj_pred.csv", full.names = TRUE)

@@

Do each feature's centile abs. error in scores change based on combat version?

Computed using `ratio_results.R`, scp'd from cubic.

```{r}
cent.feat.t.test <- readRDS(paste0(data_path, "/full_featurewise_cent_t_tests_all_out.RDS"))
names(cent.feat.t.test) <- n_perm_list
cent.feat.t.test.df <- bind_rows(cent.feat.t.test, .id="perm") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

cent.feat.t.test.df %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig=sum(sig_fdr))
```

```{r}
cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~comp)
```

look at combatGAM vs combatLS

```{r}
cent.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & comp =="cf.gamlss_cf.gam") %>%
ggplot(aes(x=perm, fill=bigger_group)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~pheno_cat)
```

Plot CT with combatGAM and combatLS on brains

```{r}
ct.t.tests <- cent.feat.t.test.df %>%
  dplyr::filter(comp =="cf.gamlss_cf.gam" & stringr::str_detect(pheno, "CT")) %>%
  mutate(label=gsub("_CT", "", pheno),
         worsefit = ifelse(sig_fdr==TRUE, bigger_group, "NS"))

ct.t.tests_to_plt <- left_join(ct.t.tests, dk.parc)

ct.t.tests_to_plt %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=worsefit)) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  facet_wrap(~perm, nrow=2)
```

@@

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
cent.diffs.v.plot <- perm_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=dataset, y=mean_cent_abs.diff, fill=perm), scale="count") +
  labs(y= "Mean Magnitude Centile Error", x = "ComBat Configurations") +
  scale_x_discrete(labels=c(dataset_names)) +
  guides(fill=guide_legend(title="Sampling \nPermutation")) + 
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations replicated 10x")
cent.diffs.v.plot
# ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot)
```

Plot raw values from random permutation

```{r, eval=FALSE}
raw_files <- list.files(path = data_path, pattern = "_diffs.csv", full.names = TRUE) %>% unlist()

diff.df.rand <- fread(raw_files[3])

diff.df.rand <- diff.df.rand %>%
  mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|perm|-", "", Source_File))

global_abs.diffs <- diff.df.rand %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("abs.diff_", pheno_list)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff") %>%
    mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         abs.diff = abs.diff*100,
         pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_), ordered=TRUE, levels=c("Global Volume", "Regional Volume", "Regional SA", "Regional CT"))) %>%
    mutate(pheno = factor(pheno, ordered=TRUE, levels=c(vol_list_global, vol_list_regions, sa_list, ct_list)))#sort w/in pheno_cat

dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
all.abs.err.plt <- global_abs.diffs %>%
  dplyr::filter(dataset != "cf") %>%
  ggplot() +
  geom_boxplot(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=abs.diff, fill=dataset), outlier.size=.1) +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  facet_wrap(~dataset, nrow=3, labeller = as_labeller(dataset_names), scales="free_y") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), ggh4x.axis.nesttext.x = element_text(angle = 90, vjust=0.4), legend.position="none")
ggsave("figs/all_abs_err_plt_wlabels.jpeg", all.abs.err.plt, width=16, height=9, units="in")
```

@@

Test w/in feature sex-biases in errors (diff_list) using `featurewise_sex_bias_test.R`, saved as `full_featurewise_cent_sex_bias_tests.RDS`

```{r}
cent.subj.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_cent_sex_bias_tests.RDS"))
cent.subj.sex.test.df <- bind_rows(cent.subj.sex.test.list)
```

simple bar-plot to count regions w sigificant sex-biases

```{r}
cent.subj.sex.test.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = c("lightblue", "red"))
```

### Without Extremes

Test differences in abs. magnitude of centile errors w/in each feature

```{r}
noext.cent.feat.t.test <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_t_tests_all_out.RDS"))
names(noext.cent.feat.t.test) <- n_perm_list
noext.cent.feat.t.test.df <- bind_rows(noext.cent.feat.t.test, .id="perm") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

noext.cent.feat.t.test.df %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig=sum(sig_fdr))
```

compare results
```{r}
noext.cent.t.test.df2 <- noext.cent.feat.t.test.df %>%
  mutate(full_df = 0)
cent.feat.t.test.df2 <- cent.feat.t.test.df %>%
  mutate(full_df = 1)

comp.df <- full_join(noext.cent.t.test.df2, cent.feat.t.test.df2)
comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(comp ~ full_df)

comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=comp, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap( ~ full_df)
```

Sex-Bias tests

```{r}
noext.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext.subj.sex.test.df <- bind_rows(noext.subj.sex.test.list)
```

simple bar-plot to count regions w sigificant sex-biases

```{r}
noext.subj.sex.test.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = c("lightblue", "red"))
```

@@

Do each feature's z-score abs. error in scores change based on combat version?

Computed using `ratio_results.R`, scp'd from cubic.

```{r}
z.feat.t.test <- readRDS(paste0(data_path, "/full_featurewise_z_t_tests_all_out.RDS"))
names(z.feat.t.test) <- n_perm_list
z.feat.t.test.df <- bind_rows(z.feat.t.test, .id="perm") %>%
  mutate(pheno = sub(".z", "", pheno)) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

z.feat.t.test.df %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig=sum(sig_fdr))
```

```{r}
z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~comp)
```

look at combatGAM vs combatLS

```{r}
z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE & comp =="cf.gamlss_cf.gam") %>%
ggplot(aes(x=perm, fill=bigger_group)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~pheno_cat)
```

```{r}
z.diffs.v.plot <- perm_subj.df %>%
  ggplot() +
  geom_violin(aes(x=dataset, y=mean_z_abs.diff, fill=perm), scale="count") +
  labs(y= "Mean Absolute Z-Score Error", x = "ComBat Configurations") +
  scale_x_discrete(labels=c(dataset_names)) +
  guides(fill=guide_legend(title="Sampling \nPermutation")) + 
  ggtitle("Within-subject mean magnitude of error in z scores across ComBat \nconfigurations replicated 10x")
z.diffs.v.plot
# ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot)
```

Test w/in feature sex-biases in errors (diff_list) using `featurewise_sex_bias_test.R`, saved as `full_featurewise_cent_sex_bias_tests.RDS`

```{r}
z.subj.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.subj.sex.test.df <- bind_rows(cent.subj.sex.test.list)
```

simple bar-plot to count regions w sigificant sex-biases

```{r}
z.subj.sex.test.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = c("lightblue", "red"))
```

### Without Extremes

Test differences in abs. magnitude of centile errors w/in each feature

```{r}
noext.z.feat.t.test <- readRDS(paste0(data_path, "/no.ext_featurewise_z_t_tests_all_out.RDS"))
names(noext.z.feat.t.test) <- n_perm_list
noext.z.feat.t.test.df <- bind_rows(noext.z.feat.t.test, .id="perm") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

noext.z.feat.t.test.df %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig=sum(sig_fdr))
```

compare results
```{r}
noext.z.t.test.df2 <- noext.z.feat.t.test.df %>%
  mutate(full_df = 0)
z.feat.t.test.df2 <- z.feat.t.test.df %>%
  mutate(full_df = 1)

z.comp.df <- full_join(noext.z.t.test.df2, z.feat.t.test.df2)
z.comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(comp ~ full_df)

z.comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=comp, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap( ~ full_df)
```

Sex-Bias tests

```{r}
noext.subj.sex.test.z.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext.subj.sex.test.z.df <- bind_rows(noext.subj.sex.test.z.list)
```

simple bar-plot to count regions w sigificant sex-biases

```{r}
noext.subj.sex.test.z.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = c("lightblue", "red"))
```
